A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-18 article/02_Materials_and_Methods.Rmd
made correlation table more nice with highlighting

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
knitr::kable(
  distance_and_correlation_table, 
  "latex", 
  caption = "Mean cultural distance, correlation and mantel test results", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace"
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type" = 3, "burial construction" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

>>>>

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean cultural distance, correlation and mantel test results", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type" = 3, "burial construction" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```
